### 2015-02-27 icfp15-servo/rust.tex
Perf numbers

\subsection{Concurrency and parallelism}
Rust contains library functionality for concurrency and data parallelism.
Concurrency, in particular, integrates cleanly with Rust's ownership types.
In safe concurrent programs, the data operated on by distinct threads is also itself distinct.
Through the use of Rust's ownership model, data cannot be owned by two threads at the same time.
For example, the following code generates a static error from the compiler because after the first
thread is spawned, the ownership of \lstinline{data} has been transferred into the closure associated
with that thread and is unavailable for transfer in to the closure for the second thread.
%http://is.gd/tkcD9R
\begin{lstlisting}
fn main() {
  let mut data = Box::new(0);

  Thread::spawn(move || {
    *data = *data + 1;
  });
  Thread::spawn(move || {
    *data = *data + 1;
  });
  print!(``{}'', data);
}
\end{lstlisting}

>>>>

\subsection{Concurrency and parallelism}
Rust contains library functionality for concurrency and data parallelism.
Concurrency, in particular, integrates cleanly with Rust's ownership types.
In safe concurrent programs, the data operated on by distinct threads is also itself distinct.
Through the use of Rust's ownership model, data cannot be owned by two threads at the same time.
For example, the code in \figref{fig:bad-concurrency} generates a static error from the compiler because
after the first thread is spawned, the ownership of \lstinline{data} has been transferred into the
closure associated with that thread and is unavailable for transfer in to the closure for the second thread.
%http://is.gd/tkcD9R
\begin{figure}
\begin{lstlisting}
fn main() {
  let mut data = Box::new(0);

  Thread::spawn(move || {
    *data = *data + 1;
  });
  Thread::spawn(move || {
    *data = *data + 1;
  });
  print!(``{}'', data);
}
\end{lstlisting}
  \caption{Code that will not compile because it attempts to access mutable state from two threads.}
  \label{fig:bad-concurrency}
\end{figure}

### 2015-02-27 icfp15-servo/servo.tex
Perf numbers

\section{Servo}
\label{sec:servo}
In this section, we cover specific areas of Servo's design or implementation that make use of Rust
and the impacts and limitations of these features.

>>>>

\section{Servo}
\label{sec:servo}
In this section, we cover specific areas of Servo's design or implementation that make use of Rust
and the impacts and limitations of these features.
The most important test for a browser, though, is performance --- Servo must be at least as fast
as other browsers at similar tasks to succeed, even if it provides additional memory safety.
\tblref{servo-perf} shows a preliminary breakdown of the performance in the layout stage (described
in \secref{sec:browsers}) of rendering several web sites, taken on a modern Macbook Pro.
\begin{table}
  \begin{center}
    \begin{tabular}{r || r | r | r}
      Site & Gecko & Servo 1 thread & Servo 4 threads \\
      \hline
      Reddit & 250 & 100 & 55  \\
      CNN & 105 & 50 & 35 \\
    \end{tabular}%
  \end{center}%
  \caption{Performance of Servo against Mozilla's Gecko rendering engine on the layout portion of some common sites.
  Times are in milliseconds.}
  \label{servo-perf}
\end{table}
